\section*{10 Hypothesis Testing and p-values}

\subsection*{Solution 6.}

I'm not sure if I understand the question correctly.
Phillips and King are interested in testing the null hypothesis $\theta \leq \frac{1}{2}$, not $\theta = \frac{1}{2}$.
The first one is statistically significant, the latter is not as you will see in the solution.

We can use the Wald test.
The null hypothesis $H_0: \theta_0 = \frac{1}{2}$.
Let $n = 1919$.
We estimate $\hat{\theta} = \frac{922}{n} \approx 0.48$.
Note that
$$
\mathrm{Var}(\theta_0)
    = \mathrm{Var}(\frac{1}{n} \sum_{i=1}^n X_i)
    = \frac{1}{n^2} \sum_{i=1}^n \mathrm{Var}(X_i)
    = \frac{1}{n^2} n \theta_0 (1 - \theta_0)
    = \frac{1}{4n}
$$
as $X_i \sim \mathrm{Bin}(n, \theta_0)$ and $\theta_0 = \frac{1}{2}$.
Wald's test statistic is then given by
$$
W = \frac{\hat{\theta} - \theta_0}{\sqrt{\mathrm{Var}(\theta_0)}}
    = 2\sqrt{n} (\hat{\theta} - \theta_0)
    \approx -1.75.
$$
The p-value is $2\Phi(|W|) \approx 0.08$.
So we do not reject the null-hypothesis.

The confidence interval for which we reject the null-hypothesis is
$$
C = (\hat{\theta} - \hat{se} z_{0.025}, \hat{\theta} + \hat{se} z_{0.025})
    = (0.480, 0.503),
$$
as $\hat{se} = \sqrt{\hat{\theta}(1 - \hat{\theta})/n}$.

\subsection*{Solution 6. Alternative solution}

We can calculate the probability directly from the biomial distribution.
The null hypothese $H_0: \theta_0 = \frac{1}{2}$.
Under $H_0$, $X \sim \mathrm{Bin}(n, \theta_0)$, where $n = 1919$.
Then the p-value is $P(X \geq 922) + P(X \leq 1919/2 - 37.5) \approx 0.087$.
So we don't reject the null-hypothesis.

We reject the null-hypothesis if
$$
    X \notin (z_{0.025}, z_{0.975}) = (917, 1002).
$$


\subsection*{Solution 7.}

See code for explicit calculations.

(a) We use the Wald test on $H_0: \overline{\Delta} = \overline{X} - \overline{Y} = 0$, where $X$ are the measurements of Twain and $Y$ the measurements of Snodgrass.
The Wald test gives us a p-value of approximately $0.00008$, so we reject the null hypothesis that the essays of Twain and Snodgrass are the same.
The confidence interval of $\overline{\Delta}$ is aproximately $(0.011, 0.033)$.

(b) Using the permutation test on $T(X_1, ..., X_8, Y_1, ..., Y_{10}) = |\overline{X} - \overline{Y}|$.
The approximate p-value is $0.00089$.
We reject the null hypothesis that the distributions of $X$ and $Y$ are the same.


\subsection*{Solution 8.}

(a) We have to find $c$ such that
$$
\alpha = P_0\left(\frac{1}{n}\sum_{i = 1}^n X_i > c\right).
$$
Note that under $H_0$, $E(\frac{1}{n}\sum_{i = 1}^n X_i) = 0$ and $\mathrm{Var}(\frac{1}{n}\sum_{i = 1}^n X_i) = \frac{1}{\sqrt{n}}$.
So
$$
P_0\left(\frac{1}{n} \sum_{i = 1}^n X_i > c\right) = P(Z > \sqrt{n}c) = \Phi(-\sqrt{n}c).
$$
Take $c = -\Phi^{-1}(\alpha)/\sqrt{n}$.

(b) Under $H_1$, $E(\frac{1}{n} \sum_{i = 1}^n X_i) = 1$ and $\mathrm{Var}(\frac{1}{n} \sum_{i = 1}^n X_i) = \frac{1}{\sqrt{n}}$.
So
$$
\beta(1) = P_1\left(\frac{1}{n} \sum_{i = 1}^n X_i > c\right) = P(Z > (c - 1)\sqrt{n}) = \Phi((1 - c)\sqrt{n}).
$$

(c) Note that for fixed $\alpha$,
$$
\beta(1) = \Phi(\sqrt{n} - c\sqrt{n}) = \Phi(\sqrt{n} + \Phi^{-1}(\alpha)).
$$
As $\Phi^{-1}(\alpha)$ is fixed $\beta(1) \to 1$ as $n \to \infty$.


\subsection*{Solution 9.}
\begin{equation*}
\begin{split}
\beta(\theta_1) &= P_{\theta_1}(|Z| < z_{\frac{\alpha}{2}}) \\
    &= 1 - P_{\theta_1}(-z_{\frac{\alpha}{2}} < Z < z_{\frac{\alpha}{2}}) \\
    &= 1 - P_{\theta_1}\left(-z_{\frac{\alpha}{2}} < \frac{\hat{\theta} - \theta_0}{\hat{se}} < z_{\frac{\alpha}{2}}\right) \\
    &= 1 - P_{\theta_1}\left(-z_{\frac{\alpha}{2}} < \frac{\hat{\theta} - \theta_1}{\hat{se}} + \frac{\theta_1 - \theta_0}{\hat{se}} < z_{\frac{\alpha}{2}}\right).
\end{split}
\end{equation*}
As $n \to \infty$, $\frac{\hat{\theta} - \theta_1}{\hat{se}} \to 0$ and $\frac{\theta_1 - \theta_0}{\hat{se}} \to \infty$, because $\hat{se} \to 0$ and $\theta_1 > \theta_0$.
Therefore $\beta(\theta_1) \to 1$ as $n \to \infty$.


\subsection*{Solution 10.}

See code.
We use three different tests: Walk test per week, binomial test per week, and the $\chi^2$-test.
All three of them suggest that in week -1 and 1 a significant change in elderly Chinese woman took place.


\subsection*{Solution 11.}

See code.
The only drugs that seems to have any significant effect is Chlorpromazine.


\subsection*{Solution 12.}

(a) Let $X_1, X_2, ..., X_n \sim \mathrm{Poison}(\lambda_0)$.
Let $\hat{\lambda} = \overline{X}$ be the MLE of $X$.
Note that
$$
\mathrm{Var}(\hat{\lambda}) = \frac{1}{n^2} \sum_{i=1}^n \mathrm{Var}(X_i) = \frac{\lambda_0}{n}.
$$
So the Wald estimate is
$$
W = \frac{\hat{\lambda} - \lambda_0}{\hat{se}} = \sqrt{n} \frac{\hat{\lambda} - \lambda_0}{\sqrt{\lambda_0}}.
$$
We reject $H_0: \lambda = \lambda_0$ if $|W| > z_{\frac{\alpha}{2}}$.

(b) See code.
For $n = 20$ we approximate that 5.62\% of all tests is rejected.
This is not exactly equal to 5\% as the Poisson distribution is only approximately similar to the normal distribution.
When $n \to \infty$ the rejection rate will go to exactly 5\%.


\subsection*{Solution 13.}

Let $X_1, X_2, ..., X_n \sim \mathcal{N}(\mu, \sigma^2)$.
We will construct a likelihood ratio test for null hypothesis $H_0: \mu = \mu_0$ against $H_1: \mu \neq \mu_0$.
Let $\hat{\mu} = \overline{X}$ be the maximum likelihood estimator for $\mu$.
Note that
$$
\ell(\mu) = -\frac{n}{2} - \mathrm{log}(\sigma) - \frac{1}{2\sigma^2} \sum_{i=1}^n (X_i - \mu)^2.
$$
So
\begin{equation*}
\begin{split}
\lambda &= 2\ell(\hat{\mu}) - 2\ell(\mu_0) \\
    &= \frac{1}{\sigma^2} \sum_{i=1}^n \left[ (X_i - \mu_0)^2 - (X_i - \hat{\mu})^2 \right] \\
    &= \frac{1}{\sigma^2} \sum_{i=1}^n (\mu_0^2 - 2(\mu_0 - \hat{\mu}) - \hat{\mu}^2) \\
    &= \frac{1}{\sigma^2} (n\mu_0^2 - 2n(\mu_0 - \hat{\mu})\hat{\mu} - n\hat{\mu}^2)
    = n \left(\frac{\hat{\mu} - \mu_0}{\sigma}\right)^2.
\end{split}
\end{equation*}
Observe that the likelihood ration and Wald statistics are related, because $\lambda = W^2$.
